---
title: "KO Mouse Data Parsing"
author: "Matthew Berginski"
output: github_document
---

```{r setup, include=FALSE}
library(DarkKinaseTools)
library(tidyverse)
library(here)
```

# Data Sources

KOMP and IMPC have already made quite a few KO mouse lines for the a range of the dark kinases. They have provided a summary of the work they have already done, so it's probably a good idea to link to the associated pages. Check out http://www.mousephenotype.org/data/secondaryproject/idg for all the associated links and information.

```{r download}
if (! file.exists(here('KO_mouse/IMPC_KO_data.tsv'))) {
  download.file('http://www.mousephenotype.org/data/secondaryproject/export/idg?fileType=tsv&fileName=idgData',
                here('KO_mouse/IMPC_KO_data.tsv'))
}
```

# DK Filtering/Output

```{r filtering_output}
mouse_KO = read.delim(here('KO_mouse/IMPC_KO_data.tsv')) %>%
  filter(Family == "Kinase")
  
```

Interestingly, they also note that there 11% of the IDG genes have no mouse homolog. Let's get the kinases out of their list.

```{r missing_genes}
#http://www.mousephenotype.org/data/secondaryproject/idg/mapping
```