---
title: "GenomeRNAi Processing"
author: "Matthew Berginski"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(here)
library(DarkKinaseTools)
library(BerginskiRMisc)
library(kableExtra)
```

# Data Source

There is a database of RNAi screens named GenomeRNAi that I'm looking to scan for the dark kinases (genomernai.org). The primary download links are broken, but I manually copied out their master list of gene hits and saved it out using calc (saved as GenomeRNAi.ods). After getting the data into the spreadsheet I added column headers and saved as csv (GenomeRNAi.csv). I should try to contact them to get a complete list, maybe...

# Read in Data and Scan for Kinases

```{r loading_filtering}
RNAi = read.csv(here('GenomeRNAi/GenomeRNAi.csv'))
kinase_RNAi = RNAi %>% 
  filter(Entrez_Gene_ID %in% all_kinases$entrez_id) %>%
  left_join(all_kinases, by=c('Entrez_Gene_ID'='entrez_id'))

dark_RNAi = kinase_RNAi %>% filter(class=="Dark")
light_RNAi = kinase_RNAi %>% filter(class=="Light")
```

OK then, there's quite a few hits (`r dim(dark_RNAi)[1]`). Let's take a look at the distribution of number of hits.

```{r hit_dist}
ggplot(dark_RNAi,aes(x=Number_of_hits)) + geom_histogram(bins=20) + theme_berginski()
```

The top ten dark kinases along with the number of hits are as follows:

```{r top_dark}
kable(dark_RNAi %>% 
        arrange(desc(Number_of_hits)) %>% 
        slice(1:10) %>%
        select(Gene,Number_of_hits))
```

# Comparison to Light Kinases

```{r light_comp}
ggplot(kinase_RNAi,aes(x=class, y=Number_of_hits)) + geom_boxplot() + theme_berginski()

ggplot(kinase_RNAi,aes(x=Number_of_hits, fill=class)) + geom_density(alpha=0.5) + theme_berginski()
```

That's pretty interesting, the light (`r dim(light_RNAi)[1]` gene represented) kinases have nearly the same distribution as the dark kinases. The mean number of hits is slightly higher (`r mean(dark_RNAi$Number_of_hits)` dark, `r mean(light_RNAi$Number_of_hits)` light), but the distributions are quite similar.